Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-07 acknowledgments.tex
added some acknowledgements. Should we also try to list all the grant numbers?

Development of \enzo\ has been supported by the National Science Foundation, the National Aeronautics and Space Administration, the Department of Energy, the University of Illinois and National Center for Supercomputing Applications, UC San Diego and the San Diego Supercomputing Center, Columbia University, Georgia Tech, Michigan State University, ...  \red{We all need to add to the acknowledgments!}

>>>>

Development of \enzo\ has been supported by the National Science
Foundation, the National Aeronautics and Space Administration, the
Department of Energy, the University of Illinois and National Center
for Supercomputing Applications, UC San Diego and the San Diego
Supercomputing Center, Columbia University, Georgia Tech, Michigan
State University, Pennsylvania State University, Stanford University,
SLAC National Accelerator Laboratory, Kavli Institute for Particle
Astrophysics and Cosmology, the Kavli Institute for Theoretical
Physics at Santa Barbara, ...  \red{We all need to add to the acknowledgments!}
